Unemployment Insurance and Spending

### 2022-02-24 outputs/paper/paper.Rmd
Add files via upload

---
title: Unemployment Insurance and Spending
author: "Marco Chau and Chyna Hui"
date: "18 February 2022"
output:
  bookdown::pdf_document2:
header-includes:
  \usepackage{float}
  \floatplacement{figure}{H}
toc = FALSE:
Abstract:

@@

# Setting working directory to data folder
setwd("C:/Users/chaum/OneDrive/Bachelor of Information School Work/Term 2/INF312/Paper 2/Consumer Spending Github/outputs/rda")

#Loading in rda files with dataframes containing data
load("clean_iandsdat.rda")
load("clean_incomedat.rda")
load("clean_spendchange.rda")
load("clean_spendchangetype.rda")
load("clean_spendingdat.rda")
load("clean_employdat.rda")
```

@@

Using the original data provided by Ganong and Noel, this paper replicates the consumer spending, income, and employment hazard metrics to expand their conclusion, arguing that a diminishing payment schedule for UI across a longer duration would be even more effective.

@@

##Graphs

@@

#Results
Results go here

#Discussion
Discussion goes here

>>>>

---
title: Unemployment Insurance and Spending
author: "Marco Chau and Chyna Hui"
date: "18 February 2022"
output:
  bookdown::pdf_document2:
header-includes:
  \usepackage{float}
  \floatplacement{figure}{H}
toc = FALSE:
abstract: Abstract goes here

@@

#Loading in rda files with dataframes containing data
load("../rda/clean_iandsdat.rda")
load("../rda/clean_incomedat.rda")
load("../rda/clean_spendchange.rda")
load("../rda/clean_spendchangetype.rda")
load("../rda/clean_spendingdat.rda")
load("../rda/clean_employdat.rda")
```

@@

Using the original data provided by Ganong and Noel, this paper replicates the consumer spending, income, and employment hazard metrics to expand their conclusion, arguing that a diminishing payment schedule for UI across a longer duration would be even more effective. To develop this argument, this paper first provides a literature review on existing theories between UI and its effects on the labour and consumption market in section \@ref(literature-review). Section \@ref(data) examines the source, methodology, ethics of the data, and the data itself provided by the original authors. In section \@ref(results), we examine how employment, spending, income, UI duration connect. Finally, in section \@ref(discussion) we discuss the possible policy implications using the relations shown in section \@ref(results).

@@

## Graphs

@@

# Results
Results go here

# Discussion
Discussion goes here

# References
